%
% hps_thesis.tex
% author: Omar Moreno 
% date: August 31, 2015
%

% Set the document type and the font size
\documentclass[12pt]{ucthesis}

\usepackage[letterpaper, left=1.50in, right=1.25in]{geometry}

% Package from AMS that facilitates formula typography
\usepackage{amsmath}

% ?
\usepackage[utf8]{inputenc}

% Package required to load images
\usepackage{graphicx}

% Package used to add hyperlinks to references within a document
\usepackage{hyperref}

\usepackage{subcaption}

\usepackage{booktabs}

\usepackage{rotating}

\usepackage{indentfirst}


% Package used to adjust the size of the section headings
\usepackage{titlesec}
\titleformat{\chapter}[display]
    {\LARGE\bfseries}{\chaptertitlename\ \thechapter}{20pt}{\LARGE}
\titleformat*{\section}{\large\bfseries}
\titleformat*{\subsection}{\normalsize\bfseries}

%\def\dsp{\def\baselinestretch{1.8}\large\normalsize}
%\dsp

\makeatletter
\let\@currsize\normalsize
\makeatother

%\usepackage{caption}

\usepackage{setspace}

%\captionsetup{font={stretch=1.0}}

\setstretch{2}

\begin{document}

%%%%%%%%%%%%%%%%
% Front Matter %
%%%%%%%%%%%%%%%%
\input{title_page}
\begin{frontmatter}

    \maketitle
    \copyrightpage
    
    \tableofcontents
    \listoffigures
    \listoftables

    %%%%%%%%%%%%%%%%
    %   Abstract   %
    %%%%%%%%%%%%%%%%
    \begin{abstract}
        \thispagestyle{plain}
        \input{chapters/abstract}
    \end{abstract}

    \begin{dedication}
        \null\vfil
        {
            \begin{center}
                To my wife Monica and son Maddox. \\
                Your love and inspiration make me feel like I can accomplish anything.
            \end{center}
        }
        \vfil\null
    \end{dedication}

    \begin{acknowledgements}
        The completion of this dissertation was due in large part to the guidance
        and support that I received from my colleagues on the Heavy Photon Search
        experiment.  Specifically, I want to thank John Jaros for taking the
        time to mentor me and instill in me valuable knowledge that I will
        continue to use in the future.  I would also like to thank Tim Nelson, 
        Per Hansson for their guidance through the construction of the Silicon
        Vertex Tracker and its data acquisition system as well as for helping me 
        keep sane during our time at JLab. I want to thank
        Mathew Graham for being the greatest of all analysis leaders and 
        guiding me through my analysis.  Of course, I can't forget to thank
        Sho Uemura and Matthew Solt for their important contributions to this analysis
        and for the fun times we shared in the office.
        

        My colleagues at the Santa Cruz Institute for Particle Physics were also
        crucial to me completing my dissertation.  Specifically, I want to thank
        Bruce Schumm for giving me the opportunity to first work on ILC hardware,
        for helping me grow as an experimentalist and for mentoring me during 
        my first few years of graduate school.
        I would like to
        thank Alex Grillo for taking the time to mentor me as well as Vitaliy Fadeyev
        who taught me the majority of the electronics knowledge I currently posses.

        Without the support of my parents, sister and nephew, I wouldn't be the person I am today.
        To my father and mother, you always encouraged me to pursue my goals 
        to the best of my ability and to work through whatever obstacles that
        life may have presented.  The strong work ethic you instilled 
        in me is one of the major reasons I was able to complete my dissertation.
        To my nephew Joseph, I have enjoyed seeing you grow intellectually these
        past few years and I'm looking forward to all the questions you will have
        once you read this dissertation. To my sister, thank you for all the support 
        you gave me during my time in graduate school.

        Finally, I want to thank my beautiful wife Monica Moreno.  Your support
        and encouragement were crucial to the completion of this dissertation.
        It's not possible to put into words what you mean to me.  I will love
        you until the end of time and I'm looking forward to the many memories 
        we will continue to share.

    \end{acknowledgements}

\end{frontmatter}

%%%%%%%%%%%%%%%%%%%%
%   Introduction   %
%%%%%%%%%%%%%%%%%%%%
\input{chapters/introduction}

\input{chapters/motivations}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  HPS Signal and Backgrounds   %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{chapters/fixed_target}

%%%%%%%%%%%%%%%%%%%%%
%   HPS Apparatus   %
%%%%%%%%%%%%%%%%%%%%%
\input{chapters/hps_apparatus}

%%%%%%%%%%%%%%%%%%%
%   Performance   %
%%%%%%%%%%%%%%%%%%%
\input{chapters/performance}

%%%%%%%%%%%%%%%%%%%%%%%
%   Event Selection   %
%%%%%%%%%%%%%%%%%%%%%%%
\input{chapters/event_selection}

%%%%%%%%%%%%%%%%%%%%%%%%
%   Resonance Search   %
%%%%%%%%%%%%%%%%%%%%%%%%
\input{chapters/resonance}

%%%%%%%%%%%%%%%%%%
%   Conclusion   %
%%%%%%%%%%%%%%%%%%
\input{chapters/conclusion}

%%%%%%%%%%%%%%%%%%%%
%   Bibliography   %
%%%%%%%%%%%%%%%%%%%%
\linespread{1}\selectfont
\bibliographystyle{hunsrt}
\bibliography{chapters/bibliography}

\end{document}
